Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-08-01 ms.tex
Allan variance for within-detector ratios

>>>>

\begin{figure*}
{\gridline{\fig{all_variance_removelinear_False_487.pdf}{0.45\textwidth}{Allan Variance}
\fig{all_variance_removelinear_True_487.pdf}{0.45\textwidth}{Allan Variance}}}
{\gridline{\fig{apratio_phot_azlab04LED1p5mAStripe64n489Rpt2TwoAp_NRC64STRIPE1P5MA}{0.7\textwidth}{Time Series of Apertures}}}
\caption{Time series for the ratio of two apertures within a detector.}\label{fig:allanVarianceWithinDetector}
\end{figure*}
